Contextual Combinatorial Cascading Bandits

### 2016-01-18 contextual combinatorial cascading bandits.tex
update proof for 'or'

\newcommand{\CLemmaPrefixExi}{
  Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
  $$
    p_{\wedge, t, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
  $$ 
}
\newcommand{\CLemmaIncre}{
  Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Then $f(A, w)$ and $f_{\wedge}(A, w)$ are increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
  $$
    f(A, w) \leq f(A, w'), ~~ f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
  $$
}
\newcommand{\CLemmaTech}{
  Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq w_1, \ldots, w_m \leq 1$, $r_1, \ldots, r_m \geq 0$ and $u_i = \min\{w_i + r_i, 1\}, 1 \leq i \leq m$. Then
  \begin{align*}
    &f(A^{(m)}, u) \leq f(A^{(m)}, w) + \sum_{k=1}^{m} \gamma_k r_k,\\
    &f_{\wedge}(A^{(m)}, u) \leq f_{\wedge}(A^{(m)}, w) + \sum_{k=1}^{m} (1 - \gamma_k') r_k,
  \end{align*}
  where $A^{(m)} = (1, 2, \ldots, m), u = (u_1, \ldots, u_m)$ and $w = (w_1, \ldots, w_m)$.
}
\newcommand{\CLemmaSumXiEstimateInDet}{
  If $\lambda \geq C_\gamma$, then
  $$
    \sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
  $$
}
\newcommand{\CLemmaDetVt}{
  $\det(\bV_t)$ is increasing with respect to $t$ and 
  $$
    \det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
  $$
}

@@

\section{Problem Formulation-general case}

We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items},  also referred to as {\em base arms}. Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$. We call each of such tuples an {\em action} of length $k$. We will use $|A|$ to denote the length of an action $A$. Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.

@@

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm. \shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be $(u_t, v_a)$ which combines both the information of the user and the base arm. \shuai{I have added one sentence.} Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user and notice that the size of the action is not fixed. Then according to the user behavior and the structure of the action $\bA_t$, we observe the weights of fist $\bO_t$ base arms in $\bA_t$. For example in website recommender systems, if the user checks from the first recommended website and stops when she finds one interesting or has checked all websites, then the observed base arms are checked websites.

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
  \label{eq:expectation}
  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.

We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$. At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.

We consider the position discount. For example in recommender systems, the positions to display advertisements might have difference prices, hence of different value when user clicks on it.

The reward function on round $t$ is an application dependent function. We assume the expected reward function $f(A, w)$ of an action $A$ with expected weights $w$ satisfy the following assumptions.

Monotonicity The expected reward $f(A, w)$ is a non-decreasing with respect to $w$. For any $d$ dimension vectors $w$ and $w'$, if $w(i) \leq w'(i)$, we have $f(A, w) \leq f(A, w')$.

Lipschitz continuity The expected reward function f(A, w) is a Lipschitz continuous with respect to $w$ together with position discount $\gamma$. In particular, there is a constant $B>0$ such that, for any $w$ and $w'$, we have
$$
	|f(A, w) - f(A, w')| \leq B\sqrt{\sum_{i \in Ind(A)} \gamma_i^2(w(i) - w'(i))^2}
$$

We don't require the agent knows how the function $f(A, w)$ is defined. We only assume the agent has access to an oracle $\cO(A, w)$. More precisely, an oracle $\cO(\cS, w)$ is  called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if given input $w$ and $\cS$, the oracle always returns an action(super arm) $A = \cO(r, \cS) \in \cS$ satisfying $f(w, S) \geq \alpha opt_{w, \cS}$ where $opt_{w, \cS} = \max_{s \in \cS}$ f(r, S).

The $\alpha$-regret on time $t$ can be written as
$$
R_t = \alpha opt_{w_t} - f(w_t, A_t).
$$
Our goal is to minimize the cumulative regret $R = \sum_{t=1}^n R_t$.

@@

At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent chooses her action. By Equation \eqref{eq:expectation}, we have 
$$
  \EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
  \{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
  \hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
  \bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a symmetric positive definite matrix. For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$.
%In the following, we will mainly use notations for the disjunctive objective when the two cases are similar.

Next we build on a good estimate of differences between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, which states the following results.

@@

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $w_{t, a} = \theta_*^{\top} x_{t,a}$ is proved in the following lemma.
\begin{lemma} %estimate of U
  \label{lem:estimateU}
  When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
  $$
    0 \leq \bU_t(a) - w_{t,a} \leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
  $$
\end{lemma}
\begin{proof}
	$w_{t, a} = \theta_*^{\top} x_{t,a}$. First by Holder's inequality,
	\begin{align*}
		\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
		&\leq \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
	\end{align*}
	Then
	\begin{align*}
		\bU_t(a) - w_{t,a} &\leq \hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}} - \theta_{\ast}^{\top}x_{t,a} \\
		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}},
	\end{align*}
	and 
	\begin{align*}
		&\bU_t(a) - w_{t,a} \\
		&\qquad \geq \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}} - \theta_*^{\top} x_{t,a}, 1 - \theta_*^{\top} x_{t,a}  \} \\
		&\qquad \geq 0		
	\end{align*}
\end{proof}

Our proposed algorithm, C$^3$-UCB, is described in Algorithm \ref{alg:ConComCascade}. First, the learning agent computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. Second, she uses the computed UCBs $\bU_t$ to select an action $\bA_t$. Third, she checks from the first base arm in $\bA_t$ and stops after checking the $\bO_t$-th base arm.
% Third, she plays $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
% $$
%   \bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
% $$ 
% or
% $$
%   \bw_t(\ba_k^t) = 0, k \leq \bO_t = \abs{\bA_t}.
% $$
Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\bbeta_t(\delta)$. 
In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like $\begin{pmatrix} A\\ B\end{pmatrix}$.

@@

To state our main theorem, we need some definitions. Let $p_{t, A}$ be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ will be observed at time $t$. Let $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed over all time. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm.

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function, with parameters $\gamma_k, k\leq K$, is a function of expected weights of base arms and satisfies the requirements stated in section 3. Assume there is an $\alpha$-approximation oracle $\cO$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB, satisfy
	\begin{align}
		R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right).
	\end{align}
\end{theorem}
\begin{proof} [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. In particular,
	\begin{align*}
    	&\EE[R(t, \bA_t)|\cH_t] \\
    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
    \end{align*}
    Also, by monotonicity and Lipschitz continuity,
    $$
    	R(t, \bA_t) \leq C \sqrt{\sum_{k=1}^{\bO_t} \bbeta_{t-1}(\delta) \| \gamma_k x_{t, \ba_k^t} \|_{\bV_{t-1}}^2}
    $$

	our analysis to that of CombCascade in \cite{kveton2015combinatorial}. This reduction is challenging for two reasons. First, our setting has contextual information. Second, we consider position-discounted weight $\gamma$.

	Our analysis can be trivially reduced to contextual combinatorial semi-bandits by conditioning on the event of observing all items. Then we can express the expected regret at time $t$ conditioned on the history $\cH_t$ as:
	\begin{align*}
    	&\EE[R(t, \bA_t)|\cH_t] \\
    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right],\\
    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
    \end{align*}
    and anaylize our problem under the assumption that all items in $\bA_t$ are observed.

@@

In the special case of single-choice-recommendations, the learning agent recommends a list of items to the user. Then the user checks from the first item and stops if she finds one interesting or has checked all items. Suppose we also consider position discount here. If the user interests in the $k$-th item, then the learning agent will receive reward $\gamma_k$. It is easy to check that in this case, the expected reward function is $f(A, w) = f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k)$. And if the parameters satisfy $1\geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$, then $f$ satisfies the requirements. (We leave all these verifications in appendix.) In this case, $p(t,A) p^* = $ Then we have
\begin{corollary}
	In the problem of single-choice-recommendations, the expected reward function is $f(A, w) = f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k)$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB, satisfy
	\begin{align}
		R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right).
	\end{align}
\end{corollary}

This reduction might be problematic because the probability $p_{\wedge, t, \bA_t}$ for the conjunctive case can be low.

>>>>

\newcommand{\CLemmaPrefixExi}{
  Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
  $$
    p_{\wedge, t, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
  $$ 
}
\newcommand{\CLemmaSumXiEstimateInDet}{
  If $\lambda \geq C_\gamma$, then
  $$
    \sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
  $$
}
\newcommand{\CLemmaDetVt}{
  $\det(\bV_t)$ is increasing with respect to $t$ and 
  $$
    \det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
  $$
}

@@

\section{Problem Formulation}

We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. Suppose we have a finite set  $E=\{1,...,L\}$ of $L$ \textit{ground items}, also referred to as {\em base arms}. Let $\Pi^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$; we call each of such tuples an {\em action} of length $k$. We will use $|A|$ to denote the length of an action $A$. Let $\Pi^{\leq K}= \cup_{k=1}^K \Pi^{k}$ denote the set of all actions with length at most $K$, and let $\cS \subseteq \Pi^{\leq K}$ be the set of \textit{feasible actions} with length at most $K$.

@@

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm. For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be the combined feature vector of base arm $a$ at time $t$. Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user. Next according to the user behavior and the stopping criterion, we observe the weights of fist $\bO_t$ base arms in $\bA_t$, which are $\bw_t(\ba_k^t), k \leq \bO_t$. For example in recommender systems, the stopping criterion might be the user finds the first interesting item or has checked all items.

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains all information as well as observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
  \label{eq:expectation}
  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. Define $w_{t,a} = \theta_{\ast}^{\top} x_{t,a}$ as the expected weight of base arm $a$ at time $t$.

We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$. At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s) \}_{k\leq \bO_s, s\leq t}$ and $\{x_t\}$, where $x_s = (x_{s,a})_{a \in E}$ denotes all context information at time $s$.

We also consider the position discount $\gamma_k, k\leq K$. For example in recommender systems, the positions to display advertisements might have difference prices, hence of different values when user clicks on.

The reward function on round $t$ is an application dependent function. We assume the expected reward function of action $A$ is a function of expected weights $w$, denoted by $f(A,w)$, and satisfies the following two assumptions.

\paragraph{Monotonicity}
The expected reward function $f(A, w)$ is a non-decreasing with respect to $w$. For any $w,w'\in \RR^E$, if $w(i) \leq w'(i)$, we have $f(A, w) \leq f(A, w')$.

\paragraph{Lipschitz continuity}
The expected reward function $f(A, w)$ is a Lipschitz continuous with respect to $w$ together with position discount parameters $\gamma_k, k\leq K$. In particular, there is a constant $B>0$ such that, for any $w,w'$, we have
$$
	|f(A, w) - f(A, w')| \leq B\sqrt{\sum_{k=1}^{|A|} \gamma_k^2(w(a_k) - w'(a_k))^2},
$$
where $A = (a_1, \ldots, a_{|A|})$.

Notice that we don't require the knowledge how $f(A, w)$ is defined. We only assume the agent has access to an oracle $\cO_{\cS}(w)$. More precisely, an oracle $\cO_{\cS}(w)$ is  called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if given input $w$, the oracle always returns an action $A = \cO_{\cS}(w) \in \cS$ satisfying $f(A,w) \geq \alpha f(A^*,w)$ where $A^* = \argmax_{A\in\cS} f(A, w)$.

The $\alpha$-regret on time $t$ can be written as
$$
R_t = \alpha f(A_t^*, w_t) - f(A_t, w_t),
$$
where $A_t^* = \argmax_{A\in\cS} f(A, w_t)$. Our goal is to minimize the cumulative regret $R(n) = \sum_{t=1}^n R_t$.

@@

At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent chooses her action. By Equation \eqref{eq:expectation}, we have 
$$
  \EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
  \{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
  \hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
  \bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a symmetric positive definite matrix. For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$. Next we build on a good estimate of the difference between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, which states the following results.

@@

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $w_{t, a} = \theta_*^{\top} x_{t,a}$ is proved in the following lemma.
\begin{lemma} %estimate of U
  \label{lem:estimateU}
  When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
  $$
    0 \leq \bU_t(a) - w_{t,a} \leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
  $$
\end{lemma}
\begin{proof}
	$w_{t,a} = \theta_*^{\top} x_{t,a}$. By Holder's inequality,
	\begin{align*}
		\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
		&\leq \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
	\end{align*}
	Then because
	\begin{align*}
		0 &\leq (\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}) - \theta_{\ast}^{\top}x_{t,a} \\
		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}
	\end{align*}
	and the definition of $\bU_t$ in \ref{lem:estimateU}, we can obtain the result.
\end{proof}

Our proposed algorithm, C$^3$-UCB, is described in Algorithm \ref{alg:ConComCascade}. First, the learning agent computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ for the expected weights of all base arms in $E$. Second, the agent uses the computed UCBs, $\bU_t$, to select an action $\bA_t = \{\ba_{1}^t,..., \ba_{\abs{\bA_t}}^t \}$. Third, the user checks from the first base arm in $\bA_t$ and stops after checking the $\bO_t$-th base arm and the agents observes $\bw_t(\ba_k^t), k\leq \bO_t$. Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\bbeta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like $\begin{pmatrix} A\\ B\end{pmatrix}$.

@@

To state our main theorem, we need some definitions. Let $p_{t, A}$ be the {\em probability of full observation of $A$}, that is the probability of observing all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ at time $t$. Let $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed over all time. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm.

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
	\end{align}
\end{theorem}
\begin{proof} [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. In particular,
	\begin{align*}
    	&\EE[R(t, \bA_t)|\cH_t] \\
    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
    \end{align*}
    Also, by monotonicity and Lipschitz continuity,
    $$
    	R(t, \bA_t) \leq B \sqrt{\sum_{k=1}^{\bO_t} \bbeta_{t-1}(\delta) \| \gamma_k x_{t, \ba_k^t} \|_{\bV_{t-1}}^2}
    $$

	% our analysis to that of CombCascade in \cite{kveton2015combinatorial}. This reduction is challenging for two reasons. First, our setting has contextual information. Second, we consider position-discounted weight $\gamma$.

	% Our analysis can be trivially reduced to contextual combinatorial semi-bandits by conditioning on the event of observing all items. Then we can express the expected regret at time $t$ conditioned on the history $\cH_t$ as:
	% \begin{align*}
 %    	&\EE[R(t, \bA_t)|\cH_t] \\
 %    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right],\\
 %    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
 %    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
 %    \end{align*}
 %    and anaylize our problem under the assumption that all items in $\bA_t$ are observed.

@@

\subsubsection{Disjunctive Objective}

In the problem of cascading recommendation, when recommended with a list of items $\bA_t = (\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$, the user checks from the first item $\ba_{1}^t$ and then one by one in order. The checking process stops if the user selects one item or has checked all items without selecting anyone. In this case, the weight of base arm $a$ at time $t$, $\bw_{t,a}$, is binary to indicate whether the user has clicked on $a$ or not. Then the random variable $\bO_t$ satisfies
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$

The agent receives some reward if the user clicks on some item: if the user clicks on the $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$. Usually the importance of the positions is decreasing: the first position is most important. So it is reasonable to assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
$$
\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
$$
where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feed back and the reward.
